### 2021-05-03 Paper/conclusion.tex
Updates from Overleaf

>>>>

The main conclusions from this paper comes from defining and  implementing an ESG factor.  In the first set of analysis where ESG term is defined as the different between the MSCI ESG index and petroleum index I observed a statistically significant result for the ESG term which matched previous work which has been conducted on ESG factor modeling. However in the second set of analysis when developing an ESG factor from the MSCI ratings I was unable to find a statistically significant factor on the aggregate level and I was only able to find a statistically significant factor for \hl{ incert number of industries}. This lack of uniformity across both definitions fosters a number of important questions to address in the implementation of FFFF models
